Why Donors Donate?

### 2020-09-09 analysis/05_market_simulator.Rmd
Added section labels for persona beta levels
updating persona beta levels
Finished persona beta levels
Fixing up persona inputs

                        "Never",

@@

                        "", 
                        # Travel to Countries
                        "Doesn't Travel", 

@@

                        "Political Preference", 

@@

                        "Trust in Political Institutions",

@@

                        "Others Should be Charitable",
                        # Worship Service Attendence
                        "Worship Service Attendence",

@@

                        "Religious Importance",

@@

                        "Chartiy Trust Importance",

@@

                        "Trust in Charity", 

@@

                        "Donation Frequency", 

@@

                        "Donation Amount",

@@

                        "Not Volunteered",

@@

                        "Volunteer Frequency",

@@

                        "Personal Activism",

@@

                        "Family Activism",
                        # Relgious Membership
                        "Religious Membership", 

@@

                        "Sport or Recreational Membership", 

@@

                        "Art, Music, or Educational Membership",

@@

                        "Labor Union Membership",

@@

                        "Political Party Membership",

@@

                        "Environmental Organization Membership",

@@

                        "Professional Association", 

@@

                        "Humanitarian or Charity Membership",

@@

                        "Consumer Organization Membership",

@@

                        "Other Organization Membership",

@@

                        "Education", 

@@

                        "Income", 

@@

                        "Age")

@@

p1_politic_pref <- reactive({
  max(input$p1_political_pref)
})

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than high school",
                     "High school",
                     "Some college",
                     "2 year degree",
                     "4 year degree",
                     "Graduate degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

@@

# Need to Fix
selectInput("p1_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

# Need to Fix
selectInput("p2_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

@@

# Need to Fix
selectInput("p3_age",
         label = "Age:",
         choices = c('Under 18',
                     '18 - 24',
                     '25 - 34',
                     '35 - 44',
                     '45 - 54',
                     '55 - 64',
                     '65 - 74',
                     '75 - 84',
                     '85 or older'))

>>>>

@@

                        "Often", 
                        # Travel to developing Countries
                        "Yes", 

@@

                        "Somewhat Liberal",
                        "Slightly Liberal",
                        "Moderate",
                        "Slightly Conservative",
                        "Somewhat Conservative",
                        "Extremely Conservative",

@@

                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust",

@@

                        "Disagree",
                        "Somewhat Disagree",
                        "Nuetral",
                        "Somewhat Agree",
                        "Agree",
                        "Strongly Agree",
                        # Worship Service Attendance
                        "At least once a month",

@@

                        "Important",

@@

                        "Very Unimportant",
                        "Somewhat Unimportant",
                        "Nuetral",
                        "Somewhat Important",
                        "Very Important",
                        "Essential",

@@

                        "Very little trust",
                        "Little trust",
                        "Nuetral",
                        "Some trust",
                        "A lot of trust",
                        "Complete trust",

@@

                        "At least once a month", 

@@

                        "$50-$99",
                        "$100-$499",
                        "$500-$999",
                        "$1,000-$4,999",
                        "$5,000-$9,999",
                        "$10,000 +",

@@

                        "Yes",

@@

                        "More than once a month, less than once a year",
                        "Atleast once a month",

@@

                        "Involved",

@@

                        "Involved",
                        # Religious Membership
                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member", 

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Inactive Member",
                        "Active Member",

@@

                        "Highschool Graduate", 
                        "Some College",
                        "2 Year College",
                        "4 Year College",
                        "Graduate or Professional Degree",
                        "Doctorate",

@@

                        "More than Median - $61,372", 

@@

                        "More than Median (> 36)")

@@

@@

# Need to Fix
selectInput("p1_education",
         label = "Education:",
         choices = c("Less than Highschool",
                     "Highschool Graduate",
                     "Some College",
                     "2 Year College",
                     "4 Year College",
                     "Graduate or Professional Degree",
                     "Doctorate"))
# Need to Fix
selectInput("p1_income",
         label = "Income:",
         choices = c('Less than $10,000',
                     '$10,000 to $19,999',
                     '$20,000 to $29,999',
                     '$30,000 to $39,999',
                     '$40,000 to $49,999',
                     '$50,000 to $59,999',
                     '$60,000 to $69,999',
                     '$70,000 to $79,999',
                     '$80,000 to $89,999',
                     '$90,000 to $99,999',
                     '$100,000 to $149,999',
                     '$150,000 to $199,999',
                     '$200,000 to $299,999',
                     '$300,000 or more'))

@@

# Need to Fix
selectInput("p1_age",
         label = "Age:",
         choices = c('Less than Median Age (< 36)',
                     "More than Median Age (> 36)"))

@@

# Need to Fix
selectInput("p2_age",
         label = "Age:",
         choices = c('Less than Median Age (< 36)',
                     "More than Median Age (> 36)"))

@@

# Need to Fix
selectInput("p3_age",
         label = "Age:",
         choices = c('Less than Median Age (< 36)',
                     "More than Median Age (> 36)"))
